---
title: "3C Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Packages
library("ggpubr")
library(psych)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(scales)
library(vtable)
#install.packages("vtable")
#install.packages("Hmisc")
#install.packages("lmtest")
#install.packages("jtools")
#install.packages("interactions")
#install.packages("lm.beta")
#install.packages("car")
#install.packages("sandwich")
#install.packages("ggrepel")
#install.package
#install.packages("pls")
install.packages("EnvStats")
library(sandwich)
library(car)
library(jtools)
library(interactions)
library(lm.beta)
library(lmtest)
library(Hmisc)
library(dplyr)
library(Metrics)
library(pls)
library(GGally)
library(EnvStats)
#library(plyr)


```
# Analyses 

# load final dataset
```{r}
omit_df <- read.csv("omit_df.csv", header=T, na.strings="")
```


# Summary statistics table

```{r}
data(omit_df)
st(omit_df, vars = c('logMeanK','GCS_index', 'Norms_index', 'Measure2_liberal_Index', 'Measure2_liberterian_Index', 'Measure2_cons_Index', 'harm_foundation', 'fairness_foundation', 'authority_foundation', 'ingroup_foundation', 'purity_foundation', 'Stress_index', 'Impacts_index', 'SDRS_Sum_scaled'))

labs <- data.frame(name1= c('logMeanK', 'GCS_index', 'Norms_index', 'Measure2_liberal_Index', 'Measure2_liberterian_Index', 'Measure2_cons_Index', 'harm_foundation', 'fairness_foundation', 'authority_foundation', 'ingroup_foundation', 'purity_foundation', 'Stress_index', 'Impacts_index', 'SDRS_Sum_scaled'), name2 = c('Temporal discounting', 'Uncertainty', 'COVID-19 social norms', 'Liberal political oreintation', 'Liberterian political oreintaiton', 'Conservative political oreintation', 'Harm Foundation', 'Fariness Foundation', 'Authority Foundation','Ingroup Foundation', 'Purity Foundation', 'COVID-19 Stress', 'COVID-19 Impact', 'Socail Deserability'))

sumtable(omit_df,
         summ =c('mean(x)',
               'sd(x)',
               'min(x)',
               'max(x)'), 
         vars = c('logMeanK', 'Norms_index','GCS_index','harm_foundation', 'fairness_foundation', 'authority_foundation', 'ingroup_foundation', 'purity_foundation', 'SDRS_Sum_scaled','Impacts_index', 'Stress_index', 'Measure2_liberal_Index', 'Measure2_liberterian_Index', 'Measure2_cons_Index'),labels =labs)

vartable <-vtable(omit_df, out = 'return')
vartable

#What about COVID DoG Mean?

(mean(omit_df$logCOVID_DoG_index))


```


# Demographics 

```{r}
#duration

mean(omit_df$Duration..in.seconds.)
sd(omit_df$Duration..in.seconds.)

#demographics

summary(omit_df$Age)
mean(omit_df$Age)
sd(omit_df$Age)
median(omit_df$Age)
max(omit_df$Age)
table(omit_df$Gender)
table(omit_df$Race)
table(omit_df$Ethnicity)
table(omit_df$Education)
table(omit_df$MaritalStatus)

#occupation and nationality were hand coded. See github readme for more info!


```

# Correlation Matrices 
```{r}

omit_df_viz <- omit_df[c(7,9,12,16, 18:20, 21:26, 32, 33)]

omit_df_viz<- rename(omit_df_viz, MCQ = logMeanK,
                     DoG = logCOVID_DoG_index,
                     Norms = Norms_index,
                     Uncert = GCS_index,
                     Libe = Measure2_liberal_Index,
                     Cons = Measure2_cons_Index,
                   Libert = Measure2_liberterian_Index,
                   Harm = harm_foundation,
                   Fair = fairness_foundation,
                   Loyal = ingroup_foundation,
                   Auth = authority_foundation,
                   pur = purity_foundation,
                  Stres= Stress_index,
                   Impac = Impacts_index,
                   Soc = SDRS_Sum_scaled)
ggpairs(omit_df_viz,
      title  = "Correlation matrix of variables",
      )
```

# Main Models of Interest 
## Hierarchical Linear Regressions, COVID DoG  

```{r}
Model0 <- lm(logCOVID_DoG_index ~ 1, data = omit_df) #to obtain Total SS

Model1 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled, data = omit_df)

Model2 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index, data = omit_df)

Model3 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index, data = omit_df)

Model4 <-lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index, data = omit_df)

Model5 <- lm(logCOVID_DoG_index ~  SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index + harm_foundation + fairness_foundation + authority_foundation + ingroup_foundation + purity_foundation, data = omit_df)

Model6 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index + harm_foundation + fairness_foundation + authority_foundation + ingroup_foundation + purity_foundation + Measure2_liberal_Index + Measure2_liberterian_Index + Measure2_cons_Index, data = omit_df)

Model7 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index + harm_foundation + fairness_foundation + authority_foundation + ingroup_foundation + purity_foundation + Measure2_liberal_Index + Measure2_liberterian_Index + Measure2_cons_Index + logMeanK, data = omit_df)
```

##Comparing SS

```{r}
anova(Model0)

#What is the SS of all the rest of the models?

anova(Model1, Model2, Model3, Model4, Model5, Model6, Model7)

#what do the individual models look like?

summary(Model1)
outlierTest(Model1)

summary(Model2)
outlierTest(Model2)

summary(Model3)
outlierTest(Model3)

summary(Model4)
outlierTest(Model4)

summary(Model5)
outlierTest(Model5)

summary(Model6)
outlierTest(Model6)

summary(Model7)
outlierTest(Model7)

```

## Hierarchical Linear Regressions, COVID DoG  w/o outliers

### Identifing outliers: Do they make a difference and if so, where? 
```{r}

#Model 1
outlierTest(Model1)

#removing outliers

omit_df_m1_outliers <-omit_df[!(omit_df$id=="59"| omit_df$id=="156" | omit_df$id=="212"),]
                                

Model1.5 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled, data =omit_df_m1_outliers)


summary(Model1.5)

#SDRS sig now

#Model 2
outlierTest(Model2)

omit_df_m2_outliers <-omit_df[!(omit_df$id=="253"),]


Model2.5 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index, data =omit_df_m2_outliers)


summary(Model2.5)

#same results as non outlier model, SDRS no longer sig

outlierTest(Model3)

omit_df_m3_outliers <-omit_df[!(omit_df$id=="253"),]

Model3.5 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index  + GCS_index, data =omit_df_m3_outliers)

summary(Model3.5)

#same results as non outlier model

outlierTest(Model4)

omit_df_m4_outliers <-omit_df[!(omit_df$id=="10"| omit_df$id=="109"| omit_df$id=="238"|omit_df$id=="253"),]

Model4.5 <-lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index, data = omit_df_m4_outliers)

summary(Model4.5)

#same results as non outlier model, but now GCS index is sig. 


outlierTest(Model5)

omit_df_m5_outliers <-omit_df[!(omit_df$id=="10" |omit_df$id=="253"),]

Model5.5 <- lm(logCOVID_DoG_index ~  SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index + harm_foundation + fairness_foundation + authority_foundation + ingroup_foundation + purity_foundation, data = omit_df_m5_outliers)


summary(Model5.5)

#same results as non outlier model, GCS index is not sig


outlierTest(Model6)

omit_df_m6_outliers <-omit_df[!(omit_df$id=="10"| omit_df$id=="238"|omit_df$id=="253"),]

Model6.5 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index + harm_foundation + fairness_foundation + authority_foundation + ingroup_foundation + purity_foundation + Measure2_liberal_Index + Measure2_liberterian_Index + Measure2_cons_Index, data = omit_df_m6_outliers)

summary(Model6.5)

#same results as non outlier model, except fairness is now trending

outlierTest(Model7)

omit_df_m7_outliers <-omit_df[!(omit_df$id=="10" |omit_df$id=="253"),]

Model7.5 <- lm(logCOVID_DoG_index ~ SDRS_Sum_scaled + Stress_index + Impacts_index +  GCS_index + Norms_index + harm_foundation + fairness_foundation + authority_foundation + ingroup_foundation + purity_foundation + Measure2_liberal_Index + Measure2_liberterian_Index + Measure2_cons_Index + logMeanK, data = omit_df_m7_outliers)

summary(Model7.5)

#same results as non outlier model

```



## Hierarchical Linear Regressions, MCQ

```{r}

MCQModel0 <- lm(logMeanK ~ 1, data = omit_df) #to obtain Total SS

MCQModel1 <- lm(logMeanK ~ SDRS_Sum_scaled, data = omit_df)

MCQModel2 <- lm(logMeanK ~ SDRS_Sum_scaled+ GCS_index, data = omit_df)

```

## Comparing SS
```{r}
anova(MCQModel0)

#Total SS is 758.7

#What is the SS of all the rest of the models?

anova(MCQModel1, MCQModel2)

#This suggests to throw out x,y ,z. 

#what do the individual models look like?

summary(MCQModel1)
outlierTest(MCQModel1)
summary(MCQModel2)
outlierTest(MCQModel2)

#no outliers! 

```

# Correlation Comparisons + general correlations for figures 

## GCS 
```{r}
ggscatter(omit_df, x = "GCS_index", y = "logMeanK", title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "Uncertainty", ylab = "Temporal Discounting")


ggscatter(omit_df, x = "GCS_index", y = "logCOVID_DoG_index", title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE,  cor.coef.coor = c(1,8), cor.method = "pearson",
          xlab = "Uncertainty ", ylab = "COVID-19 Delay of Gratification")


#Fischer-Z Comparison
paired.r(0.11, -0.022, NULL, 384)
```

## Norms
```{r}
ggscatter(omit_df, x = "Norms_index", y = "logMeanK", title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE,  cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "COVID-19 Social Norms", ylab = "Temporal Discounting")

ggscatter(omit_df, x = "Norms_index", y = "logCOVID_DoG_index", title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE,  cor.coef.coor = c(1,9), cor.method = "pearson",
          xlab = "COVID-19 Social Norms", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.078, -0.5, NULL, 384)

```

## Moral Foundations
###Fairness 

```{r}
ggscatter(omit_df, x = "fairness_foundation", y = "logMeanK", title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "Fairness Foundation", ylab = "Temporal Discounting")

ggscatter(omit_df, x = "fairness_foundation", y = "logCOVID_DoG_index",  title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,8), cor.method = "pearson",
          xlab = "Fairness Foundation", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.000, .37, NULL, 384)
```


###Loyalty 
```{r}
ggscatter(omit_df, x = "ingroup_foundation", y = "logMeanK",  title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "Loyalty Foundation", ylab = "Temporal Discounting")

ggscatter(omit_df, x = "ingroup_foundation", y = "logCOVID_DoG_index",  title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE,cor.coef.coor = c(1,9), cor.method = "pearson",
          xlab = "Loyalty Foundation", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.097, -0.19, NULL, 383)
```

## Political Orientation, Cons 
```{r}
ggscatter(omit_df, x = "Measure2_cons_Index", y = "logMeanK", title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "Conservative Political Orientation", ylab = "Temporal Discounting")

ggscatter(omit_df, x = "Measure2_cons_Index", y = "logCOVID_DoG_index", title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,9), cor.method = "pearson",
          xlab = "Conservative Political Orientation", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.036, -.37, NULL, 384)
```


## Stress 
```{r}
ggscatter(omit_df, x = "Stress_index", y = "logMeanK",  title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "COVID-19 Stress", ylab = "Temporal Discounting")

ggscatter(omit_df, x = "Stress_index", y = "logCOVID_DoG_index",  title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,9), cor.method = "pearson",
          xlab = "COVID-19 Stress", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.15, 0.25, NULL, 384)

```

#Correlation comparsions, no outliers


#lets identify the outliers via outlierTest function and a simple regression

## GCS 
```{r}
GCSModel1 <- lm(logMeanK ~ GCS_index, data = omit_df)
summary(GCSModel1)

outlierTest(GCSModel1)

#no outliers

GCSModel2 <- lm(logCOVID_DoG_index ~ GCS_index, data = omit_df)
summary(GCSModel2)

outlierTest(GCSModel2)
#again no outliers

```

## Norms
```{r}
NormsModel1 <- lm(logMeanK ~ Norms_index, data = omit_df)
summary(NormsModel1)

NormsModel2 <- lm(logCOVID_DoG_index ~ Norms_index, data = omit_df)
summary(NormsModel2)

outlierTest(NormsModel1)

outlierTest(NormsModel2)

#there are outliers identified for NormsModel2: #10, 102, 230 243

NormsModel2Outliers2 <-omit_df[!(omit_df$id=="10"| omit_df$id=="109"| omit_df$id=="238"|omit_df$id=="253"),]

ggscatter(NormsModel2Outliers2, x = "Norms_index", y = "logCOVID_DoG_index", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "COVID-19 Social Norms", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.078, -0.55, NULL, 384, n2= 380)

```

## Moral Foundations
###Fairness 

```{r}

#lets identify the outliers via CooksD and a simple regression

Fairness1 <- lm(logMeanK ~ fairness_foundation, data = omit_df)
summary(Fairness1)

Fairness2 <- lm(logCOVID_DoG_index ~ fairness_foundation, data = omit_df)
summary(Fairness2)

outlierTest(Fairness1)

outlierTest(Fairness2)

#outliers were identified: 41, 56, 243 

Fairness2Outliers2 <-omit_df[!(omit_df$id=="44"| omit_df$id=="59"|omit_df$id=="253"),]

ggscatter(Fairness2Outliers2, x = "fairness_foundation", y = "logCOVID_DoG_index", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Fairness Foundation", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.000, 0.39, NULL, 384, n2= 381)

```


###Loyalty 
```{r}

Loyalty1 <- lm(logMeanK ~ ingroup_foundation, data = omit_df)
summary(Loyalty1)

Loyalty2 <- lm(logCOVID_DoG_index ~ ingroup_foundation, data = omit_df)
summary(Loyalty2)

outlierTest(Loyalty1)

outlierTest(Loyalty2)

#outliers were identified: 10, 14, 23, 56, 149, 204 

Loyalty2Outliers2 <-omit_df[!(omit_df$id=="10"| omit_df$id=="15"|omit_df$id=="26" | omit_df$id=="59"| omit_df$id=="156"|omit_df$id=="212"),]

ggscatter(Loyalty2Outliers2, x = "ingroup_foundation", y = "logCOVID_DoG_index", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Loyalty Foundation", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.097, -0.26, NULL, 384, n2=378)




```

## Political Orientation, Cons 
```{r}

Cons1 <- lm(logMeanK ~ Measure2_cons_Index, data = omit_df)
summary(Cons1)

Cons2 <- lm(logCOVID_DoG_index ~ Measure2_cons_Index, data = omit_df)
summary(Cons2)

outlierTest(Cons1)

outlierTest(Cons2)

#outliers were identified: 10, 149, 204, 243

Cons2Outliers2 <-omit_df[!(omit_df$id=="10"| omit_df$id=="156"|omit_df$id=="212" | omit_df$id=="253"),]

ggscatter(Cons2Outliers2, x = "Measure2_cons_Index", y = "logCOVID_DoG_index", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Conservative Political Orientation", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.036, -.4, NULL, 384, n2 = 380)
```


## Stress 
```{r}

Stress1 <- lm(logMeanK ~ Stress_index, data = omit_df)
summary(Stress1)

Stress2 <- lm(logCOVID_DoG_index ~ Stress_index, data = omit_df)
summary(Stress2)

outlierTest(Stress1)

outlierTest(Stress2)

#outliers were identified:48, 243

Stress2Outliers2 <-omit_df[!(omit_df$id=="51"|omit_df$id=="253"),]

ggscatter(omit_df, x = "Stress_index", y = "logMeanK",  title = "a)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,0), cor.method = "pearson",
          xlab = "COVID-19 Stress", ylab = "Temporal Discounting")

ggscatter(Stress2Outliers2, x = "Stress_index", y = "logCOVID_DoG_index",title = "b)",
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.coef.coor = c(1,8), cor.method = "pearson",
          xlab = "COVID-19 Stress", ylab = "COVID-19 Delay of Gratification")

#Fischer-Z Comparison
paired.r(0.15, 0.3, NULL, 384, n2 =382)

```


# Misc Models
## Is age predictive of COVID DoG? 
```{r}

AgeModel <- lm(logCOVID_DoG_index ~ Age , data = omit_df)

summary(AgeModel)

plot(AgeModel)

outlierTest(AgeModel)

omit_df_age_outliers <-omit_df[!(omit_df$id=="59" | omit_df$id=="212" | omit_df$id=="10" | omit_df$id=="15" | omit_df$id=="132" | omit_df$id=="262" | omit_df$id=="156" | omit_df$id=="157" | omit_df$id=="44" | omit_df$id=="253" | omit_df$id=="26" | omit_df$id=="109" | omit_df$id=="51" | omit_df$id=="238"),]

AgeModel2 <- lm(logCOVID_DoG_index ~ Age, data = omit_df_age_outliers) 

outlierTest(AgeModel2)

summary(AgeModel2)

plot(AgeModel2)
```

## What norms are predictive of COVID DoG? 

```{r}

NormsModel1 <- lm(logCOVID_DoG_index ~ FamilyNorm_index + FriendsNorm_index + StrangerNorm_index, data = omit_df)

summary(NormsModel)

outlierTest(NormsModel1)

omit_df_norm_outliers <-omit_df[!(omit_df$id=="59" | omit_df$id=="212" | omit_df$id=="10" | omit_df$id=="15" | omit_df$id=="132" | omit_df$id=="262" | omit_df$id=="156" | omit_df$id=="157" | omit_df$id=="44" | omit_df$id=="253" | omit_df$id=="26" | omit_df$id=="109" | omit_df$id=="51" | omit_df$id=="238"),]

NormsModel2 <- lm(logCOVID_DoG_index ~ FamilyNorm_index + FriendsNorm_index + StrangerNorm_index, data = omit_df_norm_outliers) 

outlierTest(NormsModel2)

summary(NormsModel2)

```

## What does a simultaneous model look like based on what was sig in the HLR?

```{r}
MegaModel1 <- lm(logCOVID_DoG_index ~ Stress_index + Norms_index + fairness_foundation + ingroup_foundation + Measure2_cons_Index + logMeanK, data = omit_df)

summary(MegaModel1)

plot(MegaModel1)

vif(MegaModel1)

outlierTest(MegaModel1)

MM1_outliers <-omit_df[!(omit_df$id=="10" | omit_df$id=="253" | omit_df$id=="238"),] 

MegaModel2 <- lm(logCOVID_DoG_index ~ Stress_index + Norms_index+ fairness_foundation + ingroup_foundation + Measure2_cons_Index + logMeanK, data = MM1_outliers)

summary(MegaModel2)

plot(MegaModel2)

outlierTest(MegaModel2)

MegaModel3 <- lm(logMeanK ~ GCS_index, data = omit_df)

summary(MegaModel3)

outlierTest(MegaModel3)


```
